figures and calculations for global fisheries management

### 2019-01-12 documents/figs-and-calcs.Rmd
worked on fig 3

library(sf)
library(ggplot2)
#library(tmap)

@@

>>>>

library(sf)
library(ggplot2)

@@

projection_data_fig3 <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic") %>%
  group_by(IdOrig) %>% 
  filter(Year == max(Year))%>%
  filter(Dbase == "RAM") %>%
  filter(IdLevel != "Neis")

#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)

projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "0"]<- "No RBFM"
projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "1"]<- "RBFM"

fig_3 = projection_data_fig3 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 3")

fig_3
